\begin{DndMonster}{Stone Elemental}
      \DndMonsterType{Large elemental, unaligned}
  
      % If you want to use commas in the key values, enclose the values in braces.
      \DndMonsterBasics[
          armor-class = {16 (Natural Armor)},
          hit-points  = {81 \DndDice{12d10 + 15}},
          speed       = {20 ft., burrow 30 ft.},
        ]
  
      \DndMonsterAbilityScores[
          str = 18,
          dex = 7,
          con = 17,
          int = 5,
          wis = 6,
          cha = 4,
        ]
  
      \DndMonsterDetails[
          skills = {Stealth +0},
          senses = {darkvision 60 Ft., tremorsense 60 Ft., passive Perception 8},
          languages = {---},
          challenge = 3,
        ]
      % Traits
      \DndMonsterAction{Earth Glide}
      The elemental can burrow through nonmagical, unworked earth and stone. While doing so, the elemental doesn't disturb the material it moves through.
      
      \DndMonsterSection{Actions}
      \DndMonsterAction{Multiattack}
      The elemental makes two slam attacks.
  
      \DndMonsterAttack[
        name=Slam,
        distance=melee,
        type=weapon,
        mod=+4,
        reach=10,
        targets=one target,
        dmg=\DndDice{1d8+3},
        dmg-type=bludgeoning,
      ]
  
      \DndMonsterAction{Ground Pound}
      The elemental stomps the ground. Each creature around the elemental within 5 feet radius must make a DC13 dexterity saving throw or fall prone.
  
      % Legendary Actions
      \DndMonsterSection{Legendary Actions}
      The foo can take 1 legendary action, choosing from the options below. Only one legendary action option can be used at a time and only at the end of another creature's turn. The foo regains spent legendary actions at the start of its turn.
  
      \begin{DndMonsterLegendaryActions}
        \DndMonsterLegendaryAction{Shaky Ground}{A 20 feet square becomes difficult terrain until the start of the elemental's next turn.}
        \DndMonsterLegendaryAction{Rumble}{Each creature within it's lair except the elemental must make a DC 12 dexterity saving throw or gain the prone condition.}
      \end{DndMonsterLegendaryActions}
  \end{DndMonster}